Modelling participant interactions in crash severity analysis

### 2019-12-12 Interactions-Crash-Severity-v1/Interactions-Crash-Severity-v1.tex
Introduction of manuscript done, now working on background review

The rest of this paper is structure as follows. In Section
\ref{sec:review-of-methods} we present a concise review of the methods
used to analyze crash severity, with a particular focus on techniques
that consider the interactions between participants in a crash.

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{illustrative-application}{%
\section{Illustrative application}\label{illustrative-application}}

\hypertarget{further-considerations}{%
\section{Further considerations}\label{further-considerations}}

\hypertarget{concluding-remarks}{%
\section{Concluding remarks}\label{concluding-remarks}}

>>>>

The rest of this paper is structure as follows. In Section
\ref{sec:review-of-methods} we present a concise review of the methods
used to analyze crash severity, with a particular focus on techniques
that consider the interactions between participants in a crash. Section
\ref{sec:methods} describes the data conditions, preprocessing, and
approach for incorporating participant interactions in models of crash
severity. An illustrative application of the modelling strategy
described in this paper appears in \ref{sec:application}. We then
present some additional thoughts about the applicability of this
approach in Section \ref{sec:further-considerations} before offering
some concluding remarks in Section \ref{sec:concluding-remarks}.

@@

\hypertarget{sec:methods}{%
\section{Methods}\label{sec:methods}}

\hypertarget{data-considerations}{%
\subsection{Data considerations}\label{data-considerations}}

Words go here

\hypertarget{model-specification}{%
\subsection{Model specification}\label{model-specification}}

More words go here

\hypertarget{sec:application}{%
\section{Illustrative application}\label{sec:application}}

\hypertarget{data-for-the-application}{%
\subsection{Data for the application}\label{data-for-the-application}}

@@

\hypertarget{analysis-and-results}{%
\subsection{Analysis and results}\label{analysis-and-results}}

Words go here

\hypertarget{sec:further-considerations}{%
\section{Further considerations}\label{sec:further-considerations}}

Here I plan to discuss the applicability of the modelling strategy to
advanced modelling techniques (partial proportional odds, heterogeneity,
hierarchical models, etc.)

\hypertarget{sec:concluding-remarks}{%
\section{Concluding remarks}\label{sec:concluding-remarks}}
